\documentclass[compress, blue]{beamer}
\mode<presentation>
\usetheme{Warsaw}
%\usetheme{Hannover}
%\usecolortheme{lily}
\useoutertheme[subsection=false]{smoothbars}
%\useinnertheme{rectangles}
%\hypersetup{pdfpagemode=FullScreen} % makes your presentation go automatically to full screen
\setbeamertemplate{footline}[text line]{} % makes the footer EMPTY

%\usetheme{Hannover}
%\usetheme{default}
\definecolor{links}{HTML}{2A1B81}
\hypersetup{colorlinks,linkcolor=,urlcolor=links}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{mdwlist}
\usepackage{subfigure}
\usepackage[normalem]{ulem}

\newcommand{\deriv}[2]{\frac{\partial {#1}}{\partial {#2}}}
\newcommand{\xx}{{\bf x}}
\newcommand{\dx}{\delta \xx}



\begin{document}

\begin{frame}{APE - Big Idea}

Desire: Lets move away from C. Our problems are highly structured. Complex, 1000 line C programs are challenging to optimize.\\

Problem: Find a small set of operations that describe our problems well.

Our Solution: Array Primitives 

Reasoning: Arrays primitives form a particularly nice interface between
programmer and hardware. 
\begin{itemize}
\item Hails from a familiar and well used syntax (MatLab)
\item Well tuned software packages exist on a variety of architecture (i.e.
BLAS/LAPACK implemented for CPU/GPU/Cluster) 
\item Relatively predictable operation costs (memory and time) 
\item Forms a connection to Linear Algebra
\end{itemize}

\end{frame}

\begin{frame}{APE - Current Project} 

Can a computer schedule HPC code?

\end{frame}

\begin{frame}{APE - Current Proect} 

Can we go bigger? Heuristics from OR and Embedded. 

Lets raise some questions
\begin{itemize}
\item Can we do large distributed arrays? Hook up to PETSc?
\item Can we build optimized operations for specific hardware? Bootstrap?
\item What other domains use array based operations (machine learning). Can we
engage them?
\end{itemize}
\end{frame}

\begin{frame}{Project Philosophy}
We currently ave one level of compilation - gcc, gfortran, nvcc
Lets build several compilers at different levels to represent the automatable
knowledge we have. 

\begin{itemize}
\item FEM representations
\item Linear Algebra, Machine Learning, ...
\item APE, \textit{Graph Operations, String parsing (regexs)}
\item gcc, gfortran, nvcc
\end{itemize}

\end{frame}



\end{document}
